---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r processing data,echo=TRUE}
data<-read.csv('./activity/activity.csv')
data$date<-factor(data$date)
step_date<-tapply(data$steps,data$date,sum)

```
## What is mean total number of steps taken per day?
```{r total_steps, echo=TRUE,warning=FALSE,message=FALSE}
hist(step_date,breaks=40, 
     main = "Histogram of total number of steps taken per day",
     xlab = "Steps")
step_mean<-format(round(mean(step_date,na.rm=TRUE)),scientific = F)
step_median<-median(step_date,na.rm=TRUE)

```
The mean of total number of steps taken per day is `r step_mean`.
The median of total number of steps taken per day is `r step_median`.


## What is the average daily activity pattern?
```{r average_daily_activity, echo=TRUE,warning=FALSE}
data_active<-data[!is.na(data$steps),]
data_ac_by_interval<-aggregate(data_active[,c(1,3)],by=list(int = data_active$interval),mean)
with(data_ac_by_interval,
     plot(interval,steps,type="l",
          main ="A time series plot",
          xlab = "the 5-minute interval",
          ylab = "the average number of steps taken"))
int_maximum<-data_ac_by_interval$interval[which.max(data_ac_by_interval$steps)]
```
The 5 minutes interval of `r int_maximum` contains the maximum number of steps!

## Imputing missing values
```{r missing_values, echo=TRUE,warning=FALSE}
mv<-sum(is.na(data$steps))

data_na<-data[is.na(data$steps),]
mdata_na<-merge(data_na,data_ac_by_interval,by.x = 3,by.y = 3,all.y=FALSE)
newdata_na<-mdata_na[c(5,3,4)]
names(newdata_na)<-c("steps","date","interval")
newdata<-rbind(data_active,newdata_na)
newdata_date<-aggregate(newdata$steps,by=list(date_by = newdata$date),sum)
names(newdata_date)<-c("date","steps")

hist(newdata_date$steps,breaks=40, 
     main = "Histogram of total number of steps taken per day",
     xlab = "Steps")
newstep_mean<-format(mean(newdata_date$steps),scientific =FALSE)
newstep_median<-format(median(newdata_date$steps),scientific = FALSE)
```
1. the total number of missing values in the dataset is `r mv` !

4.The mean of total number of steps taken per day is `r newstep_mean`.
  The median of total number of steps taken per day is `r newstep_median`. 

## Are there differences in activity patterns between weekdays and weekends?
```{r difference_between_weekday_and_weekends, echo=TRUE,warning=FALSE}
library(lattice)
library(dplyr)
newdata$weekdays<-weekdays(as.Date(newdata$date))
newdata_weekend<-mutate(newdata,weekend = if_else(weekdays =="Sunday"|weekdays =="Saturday",
                   "Weekend","Weekday"))
nd_wd_int<-aggregate(newdata_weekend[,1],
                     by=list(newdata_weekend$interval,newdata_weekend$weekend),
                     mean)
names(nd_wd_int)=c("interval","weekend","steps")
xyplot(steps~interval|weekend, nd_wd_int,type="l",layout=c(1,2),
       xlab = "the 5-minute interval",
       ylab = "the average number of steps taken")

```

